### 2018-11-12 Sabanci_talk/Sabanci_talk.tex
Early draft finished

\begin{frame}{Motivation: Multi-messenger Astronomy}
  \begin{itemize}
    \item \emph{Multi}: two fundamentally different waves from common events.
    \item[]\quad Gravitational waves (GWs): ``hearing''  the universe.
    \item[]\quad Electromagnetic waves (EWs): ``seeing'' the universe.
    \item \red{GW170817}-\bl{GRB170817A}-\textcolor{brown}{AT2017gfo}: the ``event'' \\
    \quad inspiral + merger of two neutron stars (GWs) \\
    \ \ = short-hard gamma-ray burst + kilonova (EWs)
    \item[] Broad-band in gravitational waves: 10Hz - 2000Hz
    \item[] Ultra broad-band in electromagnetic waves: gamma rays to radio.
    \item A simple question \\
    {\small ``What can we offer to the astronomy community with future GW detections?''}
    Advance warning!
  \end{itemize}
\end{frame}

@@

\begin{frame}{The era of Einstein Telescope}{Black hole - neutron star binaries}

>>>>

\begin{frame}{Motivation: Multi-messenger Astronomy}
  \begin{itemize}
    \item \emph{Multi}: two fundamentally different waves from common events.
    \item[]\quad Gravitational waves (GWs): ``hearing''  the universe.
    \item[]\quad Electromagnetic waves (EWs): ``seeing'' the universe.
    \item \red{GW170817}-\bl{GRB170817A}-\textcolor{brown}{AT2017gfo}: the ``event'' \\
    \quad inspiral + merger of two neutron stars (GWs) \\
    \ \ = short-hard gamma-ray burst + kilonova (EWs)
    \item[] Broad-band in gravitational waves: 10Hz - 2000Hz
    \item[] Ultra broad-band in electromagnetic waves: gamma rays to radio.
    \item A simple question \\
    {\small ``What can we offer to the astronomy community with future GW detections?''}
    \item[] \red{GRB Forecasts!}
  \end{itemize}
\end{frame}

@@

\begin{frame}{Black hole - neutron star binaries}{Forecasting \red{tidal disruption} events}
  Necessary, but insufficient \bl{condition}:
  $   \f{M_\text{BH}}{M_\text{NS}} \gtrsim \left(\f{r}{R_\text{NS}}\right)^3  $
  %
  \onslide<2->
  \begin{itemize}
  \item Small separation $r\to r_\text{ISCO}$
  \item Low black hole mass, stellar evolution models: $M_\text{BH}\gtrsim 5M_\odot$
  \item High black hole spin: $\tilde{r}_\text{ISCO}\to 1$ from 6.
  \item Larger neutron star radii, $r_\text{NS}\sim15\,$km
  \end{itemize}
  \onslide<3->
  $\red{5} M_\odot -1.4 M_\odot$ BH-NS inspirals are \red{faster} because $\tau_\text{insp} \propto M^{-5/3}$
  %
  \onslide<4->
  \begin{footnotesize}
  \begin{table}[h]
  \centering
  \begin{tabular}{lccccc}
  %toprule
  \hline\hline
  $D\,$(Mpc) & \multicolumn{2}{c}{ET-B} &  & \multicolumn{2}{c}{ET-C}\T\B\\
  \hline
  {}&  \ \hspace{6mm}$T_\text{AW}$ \hspace{8mm} & $\bar{\rho}_{F}$ &{}  & $\hspace{6mm}T_\text{AW} \hspace{10mm}$ & $\bar{\rho}_{F}$\T\B\\
  %
  100 &   28.2\,minutes & 503 &{\qquad} &  2.15\,hours & 601\T\\
  200 & 8.21\,minutes & 251  &{\qquad} & 1.10\,hours & 300 \\
  %400 &  2.00\,minutes & 124 &{\qquad} & 34.2\,minutes & 148\\
  %1000 & 14.3\,seconds & 49 &{\qquad} & 13.9\,minutes& 58.5\\
  \hline\hline
  %bottomrule
  \end{tabular}
  \end{table}
  \end{footnotesize}
  %
  \onslide<5->
  $T_\text{AW} \gtrsim 1\,$hour $\Longrightarrow D \lesssim 200\,$Mpc \\
  O1 rate $R < 3600 \text{Gpc}^{-3}\text{yr}^{-1} \Longrightarrow 30\text{yr}^{-1}$ within $(200\,\text{Mpc})^3$ \\
  BH population studies: $\Longrightarrow \text{ \red{Forecast} } \red{3}\text{yr}^{-1}$ within $(200\,\text{Mpc})^3$
  % 
  %
  \begin{tikzpicture}[overlay,remember picture]
	  \onslide<1->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(5.6cm,2.25cm)}]current page.center) {\includegraphics[height=2.8cm]{figs/BH_NS_1.png}};
	  \node[anchor=center,scale=0.5,opacity=1] at ([shift={(5cm,0.7cm)}]current page.center) {Phys.Rev. D92 (2015) 044028};
  \end{tikzpicture}
\end{frame}

\begin{frame}{}{}%{Summary and Outlook}
{\bf Summary}
\begin{itemize}
 \item \bl{Quadrupole} + \bl{Newtonian} evolution = inspiral time $\tau_\text{insp}\propto \red{f^{-8/3}}$
 \item Detector sensitivity + GW strain = advance warning time $T_\text{AW}$
 \onslide<2->
 \item Advanced LIGO-Virgo will detect \bl{many} BNS, but NOT forecast.
 \onslide<3->
 \item Einstein Telescope will \bl{detect} $\bl{\ord(1000)}$ of BNS out to 1\,Gpc .
 \item Einstein-C will \red{forecast $\ord(100)$ BNS} with $T_\text{AW}>1\,$hour.
 \item Additionally forecast $< \ord(10)$ tidal disruption events.
 \item 5 to 10 BNS inspirals will be \red{localized} to $\red{10\,\text{deg}^2}$.
 \end{itemize}
 \onslide<4->{
  {\bf Outlook}
  \begin{itemize}
    \item Forecast/localize $\Rightarrow$ Mobilize EM telescopes \\
  \hspace{-5.6mm}$\Rightarrow$ \red{Observe} the merger/kilonova from  $\gamma$-rays to radio
  \item Pre-, post-merger image comparisons with LSST
 }
 \onslide<5->
 \item Contaminants? Type Ia supernovae, AGN, CV
\end{itemize}
\begin{tikzpicture}[overlay,remember picture]
	  \onslide<5->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-2.6cm,-3.8cm)}]current page.center) {\includegraphics[height=1.2cm]{figs/AAletter.png}};
	  \onslide<5->\node (img1 )[anchor=center,scale=1,opacity=1] at ([shift={(4.6cm,-3.cm)}]current page.center) {\includegraphics[height=2.7cm]{figs/SNIa_lim22mag.pdf}};
\end{tikzpicture}
